Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-11-24 paper-webserver.tex
START: working on changes to the Discussion

Future work will focus on adding additional analyses modules, using machine learning and artificial neural networks to aid genotype to phenotype predictions, and supporting different species. While the integrated approach or storing and retrieving results provides enormous benefits, the developed analyses modules are self-contained and can easily be integrated into existing platforms such as Galaxy \cite{goecks2010galaxy}, and IRIDA. The website and source code are available at \url{https://lfz.corefacility.ca/superphy/spfy/}.

@@

\section{DISCUSSION}

% drawbacks - big data
Many previous bioinformatics software programs have been developed \textit{ad hoc}, without the use of software engineering principles \cite{de2015trends}.
Such tools were often script-based, with custom data formats, and only suitable for small collections of data \cite{de2015trends}.
While this was acceptable for smaller analyses, bioinformatic pipelines utilizing WGS data are larger and involve linked dependencies, which require the application of systems engineering principles \cite{schatz2015biological}.
Additionally, many subsets of biology now require the analyses of big-data, where the ability to perform computations in real-time, store data in flexible databases, and utilize a common application programming interface (API) linking resources are required \cite{swaminathan2016review}.

One of the key goals in developing Spfy is to maintain instantaneity, as modern websites have accustomed users to instant results.
We attempt to use innovations in web development to bring a similar experience to Spfy as a predictive genomics platform for \textit{E. coli}.
% Mention where users / developers can find documentation
Spfy's main documentation and codebase are provided at \url{https://github.com/superphy/backend} and a developer guide is provided at \url{https://superphy.readthedocs.io/en/latest/}.

>>>>

Future work will focus on adding additional analyses modules, using machine learning and artificial neural networks to aid genotype to phenotype predictions, and supporting different species. While the integrated approach or storing and retrieving results provides enormous benefits, the developed analyses modules are self-contained and can easily be integrated into existing platforms such as Galaxy \cite{goecks2010galaxy}, and IRIDA. The website is available at \url{https://lfz.corefacility.ca/superphy/spfy/}. Spfy's codebase is provided at \url{https://github.com/superphy/backend} and a developer guide is provided at \url{https://superphy.readthedocs.io/en/latest/}.

@@

\section{DISCUSSION}
% Gist, we address the the "Limitations" of \cite{de2015trends}.
% Namely:
% 1. Custom formats.
% 2. Use of legacy tech (SQL) means youu can't accomadate "Big-Data" goals.

% drawbacks - big data
Many previous bioinformatics software programs have been developed \textit{ad hoc}, with inividual researchers and laboratories developing software specific to their environment \cite{de2015trends}.
Such tools were often script-based, with custom data formats, and only suitable for small collections of data \cite{de2015trends}.
While this was acceptable for smaller analyses, bioinformatic pipelines utilizing WGS data are larger and involve linked dependencies, which require the application of systems engineering principles \cite{schatz2015biological}.
Additionally, many subsets of biology now require the analyses of big-data, where the ability to perform computations in real-time, store data in flexible databases, and utilize a common application programming interface (API) linking resources are required \cite{swaminathan2016review}.

One of the key goals in developing Spfy is to maintain instantaneity, as modern websites have accustomed users to immediate results.
We attempt to use innovations in web development to bring a similar experience to Spfy as a predictive genomics platform for \textit{E. coli}.
The use of Docker containerization, task queues, and a graph database, were all chosen to support \textit{instantaneity}; modern analytics platforms must respond to user-requested analyses of big-data in the same efficiancy as old analyses of single files.
